Explaining Noord-Holland house prices

### 2023-03-30 Paper/paper.Rmd
paper layout update

@@

```{r test1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
tm_shape(funda_data) +
  tm_dots()
```

@@

```{r test2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
tm_shape(funda_data) +
  tm_dots()
```

>>>>

Plot in text

```{r test3, message=FALSE, warning=FALSE, include=FALSE}
pdf("figures/plot.pdf")
tm_shape(funda_data) +
  tm_dots(c("price", "living_area"))
dev.off()
```

\begin{figure*}
  \centering
  \includegraphics[width=.6\linewidth]{figures/plot.pdf}
  \caption{This is a figure.}
\end{figure*}

@@

```{r test1, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Figure number, Plot of NH"}
tm_shape(funda_data) +
  tm_dots()

```{r foo, out.width="100%", fig.cap="An example image.", include=FALSE, echo=FALSE}
knitr::include_graphics("figures/plot.pdf")
```

@@

```{r test2, echo=FALSE, message=FALSE, warning=FALSE, fig.cap = "Plot of NH full page"}
tm_shape(funda_data) +
  tm_dots()
```
